---
title: "EAS508-Q9"
Author: Saish Mandavkar
output: html_notebook
---

Question 9

This exercise involves the `Auto` data set available as `Auto.csv` available on the textbook website. Remove the missing values from the data.

```{r}
# Loading data and removing missing values.

Auto <- read.csv("Auto.csv", header = TRUE, na.strings = "?", stringsAsFactors = T)
Auto <- na.omit(Auto)
dim(Auto)
```

```{r}
# Head of data

head(Auto)
```

| a. Which of the predictors are quantitative, and which are qualitative?

<br>

    mpg, cylinders, displacement, horsepower, weight, accelaration, year are quantitative predictors.

    name, origin are qualitative predictors. 

<br>

b.  What is the *range* of each quantitative predictor?

<br>

```{r}
#Grouping together all the quantitative predictors
quantitative_predictors <- which(names(Auto) %in%
                                   c("mpg","cylinders","displacement","horsepower", "weight","acceleration","year"))
      
quantitative_predictors
```

<br>

```{r}
# Find the range for all using sapply and range function.

sapply(Auto[, quantitative_predictors], range)
```

<br>

c.  What is the mean and standard deviation of each quantitative predictor?

<br>

```{r}
# FInd the mean for all quantitative predictors using mean function.

sapply(Auto[, quantitative_predictors], mean)
```

```{r}
# Find the standard deviation for all quantitative predictors using sd function.

sapply(Auto[, quantitative_predictors], sd)
```

<br>

d.  Now remove the 10th through 85th observations. What is the range, mean, and standard deviation of each predictor in the subset of the data that remains?

<br>

```{r}
#Mean after removing 10-85th observations

sapply(Auto[-seq(10, 85), quantitative_predictors], mean)
```

```{r}
#Standard deviation after removing 10-85th observations

sapply(Auto[-seq(10, 85), quantitative_predictors], sd)
```

<br>

e.  Using the full data set, investigate the predictors graphically, using scatterplots or other tools of your choice. Create some plots highlighting the relationships among the predictors. Comment on your findings.

<br>

```{r}
# Scatter plot matrix for all the quantitative predictors.

pairs(Auto[ , quantitative_predictors])
```

```{r}
# Relation between cylinders and horsepower

plot(Auto$horsepower~Auto$cylinders, col = 2, main = "Horsepower vs Cylinders", xlab = "Cylinders", ylab = "Horsepower")
```

| **Cars with 8 cylinders have higher horsepower.**

```{r}
# Relation between mpg and horsepower

plot(Auto$horsepower~Auto$mpg, col = 6, main = "Horsepower vs MPG", xlab = "MPG", ylab = "Horsepower")

```

| **Cars with lower MPG have higher horsepower.**

```{r}
# Relation between MPG and weight.

plot(Auto$mpg~Auto$weight, col = 5, xlab = "Weight", ylab = "MPG", main = "Weight vs MPG")
```

| **Cars with higher weight have lower MPG.**

```{r}
plot(Auto$mpg, Auto$year, col = "blue2", xlab = "MPG", ylab = "Launch Year")
```

| **Cars are getting efficient over time.**

```{r}
hist(Auto$mpg,col=3, main = "Distribution of MPG", xlab = "MPG")
```

f\. Suppose that we wish to predict gas mileage (`mpg`) on the basis of the other variables. Do your plots suggest that any of the other variables might be useful in predicting `mpg`? Justify your answer.

| **Yes there are predictors who hold a relation with the mpg outcome, both positive and negative.**
| 
| **Example of negative relationship is Weight vs MPG, the heavier the car gets, the lower is the MPG of that car. Also, horsepower holds a negative relation with the mpg outcome, more the horsepower, less is the MPG of the car.**
| 
| **Example of a positive relationship is year vs MPG, as the time passes i.e. as the year increases, MPG tends to decrease.**
