---
title: "EAS508-Q9"
Author: Saish Mandavkar
output: html_notebook
---

Question 9

This exercise involves the `Auto` data set available as `Auto.csv` available on the textbook website. Remove the missing values from the data.

```{r}
# Loading data and removing missing values.

Auto <- read.csv("Auto.csv", header = TRUE, na.strings = "?", stringsAsFactors = T)
Auto <- na.omit(Auto)
dim(Auto)
```

```{r}
# Glimpse of data using dplyr.

glimpse(Auto)
```

| a. Which of the predictors are quantitative, and which are qualitative?

<br>

    mpg, cylinders, displacement, horsepower, weight, accelaration, year are quantitative predictors.

    name, origin are qualitative predictors. 

<br>

b. What is the *range* of each quantitative predictor?

<br>

```{r}
#Grouping together all the quantitative predictors
quantitative_predictors <- which(names(Auto) %in%
                                   c("mpg","cylinders","displacement","horsepower", "weight","acceleration","year"))
      
quantitative_predictors
```
<br>

```{r}
# Find the range for all using sapply and range function.

sapply(Auto[, quantitative_predictors], range)
```
<br>

c. What is the mean and standard deviation of each quantitative predictor? 

<br>

```{r}
# FInd the mean for all quantitative predictors using mean function.

sapply(Auto[, quantitative_predictors], mean)
```

```{r}
# Find the standard deviation for all quantitative predictors using sd function.

sapply(Auto[, quantitative_predictors], sd)
```
<br> 

d. Now remove the 10th through 85th observations. What is the range, mean, and standard deviation of each predictor in the subset of the data that remains?

<br>

```{r}
#Mean after removing 10-85th observations

sapply(Auto[-seq(10, 85), quantitative_predictors], mean)
```
```{r}
#Standard deviation after removing 10-85th observations

sapply(Auto[-seq(10, 85), quantitative_predictors], sd)
```
```

